

\section*{Biographical Sketch}
\addcontentsline{toc}{chapter}{Biographical Sketch}

Sreyoshi Sur attended the St. Xavier's University, Kolkata for her undergraduate 
studies beginning July, 2008. She received her Bachelor of Science Degree in June 
2011 with Chemistry (Hons.). Next, she joined the Chemistry department in the Indian 
Institute of Technology(IIT), Kanpur to pursue her Master's degree. While pursuing 
her degree at IIT she received the Postgraduate Merit fellowship from the University 
Grants Commission, India. In 2013 she submitted her Master's thesis and came to the 
University of Rochester to join the Biological Chemistry program in the Department of
Chemistry. She got her second Master's degree in Chemistry in 2015 while working at Alan Grossfield's lab in the Department of Biochemistry and Biophysics. She received the Department of Chemistry National Travel Award in 2016, Elena Gilde Trainee award from the Department of Biochemistry and Biophysics in 2017 and the Graduate Student Association Travel award from the Art, Science and Engineering School in 2019. She worked at the Merck Research Laboratory, West Point campus in Summer 2019 as a research intern.

\noindent \textbf{Publications}


Sur, S., Romo, T. D., and Grossfield, A., 
\emph{Selectivity and mechanism of fengycin, an antimicrobial lipopeptide, from molecular dynamics}, J. Phys. Chem. B, 2018, 122, 2219-2226\\
Sur, S., Salas-Estrada, L. and Grossfield, A.,
\emph{Effects of Cholesterol on the mechanism of fengycin, a biofungicide},
Biophys. J. 2019

\newpage